Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
tweak

The model is given by the interpretation function $\interp{-}_n$
(where $n$ is the maximum dimensionality of the specification being
modelled) mapping closed\footnote{That is, we assume that there are no
  occurrences of \textit{rvar} in a specification being modelled.  Any
  \emph{open} specification containing region variables can be made
  closed by straightforward syntactic substitution with a (closed)
  \textit{region}.} specifications to sets of
$n$-dimensional indexing schemes. The interpretation is overloaded on
\emph{regions} in Figure~\ref{fig:region-model} and on the top-level
of a specification \textit{spec} in Figure~\ref{fig:spatial-model}.

>>>>

The model is given by the interpretation function $\interp{-}_n$
(where $n$ is the maximum dimensionality of the specification being
modelled) mapping closed\footnote{That is, we assume there are no
  occurrences of \textit{rvar} in a specification being modelled.  Any
  \emph{open} specification containing region variables can be made
  closed by straightforward syntactic substitution with a (closed)
  \textit{region}.} specifications to sets of
$n$-dimensional indexing schemes. The interpretation is overloaded on
\emph{regions} in Figure~\ref{fig:region-model} and on the top-level
of a specification \textit{spec} in Figure~\ref{fig:spatial-model}.
